\vspace{0.75em}

\noindent
\textbf{BorgWarner Inc.} \hfill Auburn Hills, MI \\
\textit{Senior Software Engineer} \hfill April 2017 - May 2022 \\
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Led cross-functional software teams including cybersecurity, application diagnostics, and software integration teams, coordinating deliverables and ensuring alignment with release plans and project objectives.
    \item Took full ownership of AUTOSAR diagnostic stack and middleware software modules across multiple projects, demonstrating leadership and accountability in safety-critical software delivery.
    \item Spearheaded middleware and driver development for embedded systems, including Infineon power management IC (TLF35584) and external memory drivers with SPI to QuadSPI migration.
    \item Led collaboration with System Engineering teams to identify and clarify diagnostics requirements, taking point on UDS, OBD, and fault management modules within ISO 26262 and ASPICE frameworks.
    \item Spearheaded software module design collaboration with architects, ensuring solutions met project objectives through determined effort and cross-functional coordination.
    \item Independently implemented and developed safety-critical software based on requirements, completing complex tasks with persistence and attention to detail.
    \item Led comprehensive unit testing and integration testing initiatives, taking responsibility for ensuring software met design specifications and safety standards.
    \item Took initiative in coordinating with testing teams, leading diagnostic feature validation efforts across system components and multiple stakeholder groups.
    \item Demonstrated leadership in managing software releases, ensuring deliverables met project and customer expectations through determined project ownership and risk management.
\end{itemize}

\vspace{0.5em}

\noindent
\textit{Software Engineer II} \hfill Nov. 2015 - April 2017 \\
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Took initiative in determining customer requirements for embedded software development, demonstrating proactive problem-solving.
    \item Led software integration efforts using AUTOSAR Basic Software with GM SUM for All Wheel Drive ECM, completing complex technical challenges.
    \item Led board bring-up activities for multiple microcontroller platforms including Infineon TC23x/TC27x, ensuring successful hardware-software integration.
    \item Spearheaded focus on CAN networks, UDS diagnostics, and cyber-security, taking ownership of critical system components.
    \item Demonstrated determination in ECU requirements engineering, design, testing, and release processes, ensuring quality deliverables.
    \item Took responsibility for hardware design verification, independently ensuring schematic accuracy and functionality.
\end{itemize}