% Work Experience section for resume
\section*{Work Experience}

\noindent
\textbf{IAV Inc.} \hfill Nortville, MI \\
\textit{AI Mentor} \hfill April 2025 - Present \\
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Spearheaded AI adoption initiative across the organization, taking point on building a culture where teams confidently adopt AI tools in their daily work.
    \item Led comprehensive training programs and shared practical AI knowledge through workshops, e-learning facilitation, and hands-on coaching.
    \item Independently developed training materials, guides, and FAQs that provide actionable support for AI tool adoption.
    \item Proactively gathered feedback and identified improvement opportunities in AI implementation processes through determined analysis.
    \item Took initiative to connect with strategy teams on new tools and use cases, ensuring alignment with organizational goals.
    \item Built and fostered AI community through Q\&A sessions and peer learning initiatives, demonstrating collaborative leadership.
    \item Maintained responsibility for keeping 50+ team members updated on AI trends, achieving measurable adoption results through persistent engagement.
\end{itemize}

\vspace{0.5em}

\noindent
\textit{Senior Software Engineer} \hfill May 2022 - Present \\
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Led requirement generation initiatives across multiple projects, taking ownership of ensuring precise alignment with client needs and product goals.
    \item Spearheaded software architecture design for complex projects, demonstrating leadership in improving system efficiency for diverse customer requirements.
    \item Took point on implementing and testing safety-critical embedded software, ensuring products met reliability standards and safety compliance through determined effort.
    \item Proactively engaged with clients to troubleshoot hardware issues, building strong relationships and ensuring project success through persistent problem-solving.
    \item Led development of robust, scalable software using ASPICE processes, maintaining high standards through individual initiative and team collaboration.
    \item Conducted projects within the ASPICE framework, ensuring software was delivered with reliability, traceability, and quality standards.
    \item Took ownership of device driver and middleware development for CAN, LIN, and vehicle network protocols, completing complex tasks independently.
    \item Led thorough software requirement reviews with stakeholders, ensuring feasibility and alignment through determined collaboration.
    \item Demonstrated leadership in code reviews, promoting best practices and continuous improvement while building team camaraderie.
    \item Took initiative in developing comprehensive documentation, ensuring project transparency and knowledge sharing for ISO compliance.
    \item Led participation in quality testing initiatives, taking responsibility for validation test plans and ensuring reliable outcomes.
    \item Proactively consulted with other teams, business units, and departments on software processes, AUTOSAR implementation, and software design, demonstrating cross-functional leadership and technical expertise.
\end{itemize}